\newpage
\chapter*{Future Work}
\addcontentsline{toc}{chapter}{6. Future Work}

%\begin{itemize}
%  \item sum up the answers to all the questions
%  \item state contributions again
%  \item where my work fits in the grander scheme
%  \item further work
%\end{itemize}

The original plan of the framework was to create a documentation website showcasing the framework, and detailing everything about the framework with code snippets, and examples of usage. When the framework was being developed, a kitchen sink website was created first to ensure that the development was working as it should. Due to time constraints, a finished website fully demonstrating the framework hasn't been developed, currently a single page website used for testing has been built with all the features of the framework akin to a kitchen sink example. 

For the continuation of the project, a website will be built using the framework, and have documentation on each of the core functionality of the framework. In continuing the developing the framework, the following features would be added to the framework to make it more robust, and eliminate the need to write extra \gls{CSS}:
\begin{itemize}
	\item Badges to show unread content or to be used to display notifications
	\item Breadcrumbs to show the user where they are on a website
	\item Tabs for tabbed navigation
	\item Off canvas sidebar that slides in and out of a page, ideal for mobile design
	\item Modal to create modal dialog boxes
	\item Inverse to reverse the style of any component for light or dark backgrounds
\end{itemize}

Another feature that would be of benefit to the framework, would be the continuation of the themes. As mentioned previously the themes are quite sparse, they are only effecting the visible elements. For future work, these themes would effect all elements that are in a generic framework. 

Currently, the framework can be installed using \gls{NPM}. The goal was to build a full \gls{CLI} that using the command line, a template and theme could be downloaded using the terminal. But due to time constraints only the \gls{NPM} was developed. 


\newglossaryentry{NPM}
{
  name={rem},
  description={Node Package Manager},
  sort=NPM
}

In addition to \gls{CSS}, jQuery features to be added that would help the framework work more seamlessly such as making links active in the navigation bar, ensuring that the footer section always stays at the bottom of the page, regardless of page height, adding close options to the alerts, etc. 

%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%

%\subsection*{Creating Spectrograms with HackRF}
%\addcontentsline{toc}{subsection}{Creating Spectrograms with HackRF}
