\newpage
\chapter*{Proposal}
\addcontentsline{toc}{chapter}{Proposal}
% Chapter for each research question
% how we validated it and proved it worked

For the purposes of this assignment, a group was formed of two members, Erica Chai (2003209), and Michael Taylor (20064376). The students plan on creating a collaborative office startup organisation called Fundamentals. 

The students want to design, and create work spaces for individuals who want to work for themselves, but not alone. The students want to design, and create an exceptional workhub for curious entrepreneurs, creative startups, and determined teams. 

The research methodology that the students are planning on using for this assignment is a mixture of theoretical analysis, and quantitive. With theoretical analysis; selection and discussion of theoretical material and descriptive material, in context of setting up a company. With quantitive looking at aspects such as social trends, policy implications, business plans, and funding.\\


The areas that the students plan on covering in the report are:
\begin{itemize}
	\item Research; ensuring that their idea is a viable product, market research, who the customers are 
	\item The business itself; where to base the company, what competition is there
	\item Sources of Assistance; researching schemes and venture funds that the students could apply to for capital.
	\item The business plan
	\item Raising finance, learning and understanding equity, and debt
	\item Legal and Tax affairs; how to set up the company as a partnership, registering for VAT, and corporate tax
	\item Other affairs such a choosing an accountant, solicitor, and company administration. 
\end{itemize}

In order to gain a better understanding of enterprise development, the students have started to look into starting a business in Ireland by researching books such as \emph{The First 12 Months} \citep{bangs-90}, \emph{Starting A Business in Ireland} \citep{kane-98}, \emph{The Lean Startup} \citep{ries-11} to gain a better understanding of the steps required to build a business, and sow the seeds for that business to be successful. 